Explore tumor cell classification with CellAssign

### 2024-05-07 analyses/ewings-cell-type/02-cellassign-tumor-cell-classification.Rmd

```{r}
# heatmap of prediction scores 
tumor_predictions |>
  dplyr::select(-barcode) |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE)
```

@@

```{r}
# heatmap of prediction scores 
filtered_predictions |>
  dplyr::select(-barcode) |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE)
```

@@

filtered_celltype_assignments <- filtered_celltype_assignments |> 
  dplyr::rename(filtered_cellassign_annotations = celltype)

@@

```{r}
# heatmap of prediction scores 
visser_predictions |>
  dplyr::select(-barcode) |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE)
```

@@

```{r}
# heatmap of prediction scores 
panglao_predictions |>
  dplyr::select(-barcode) |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE)
```

>>>>

# get annotations for heatmaps
annotation_df <- data.frame(
  marker_gene_classification = classifications_df$marker_gene_classification,
  row.names = classifications_df$barcodes
)

# heatmap of prediction scores 
tumor_predictions |>
  tibble::column_to_rownames("barcode") |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE,
                     annotation_row = annotation_df)
```

@@

```{r}
# heatmap of prediction scores 
filtered_predictions |>
  tibble::column_to_rownames("barcode") |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE,
                     annotation_row = annotation_df)
```

@@

```{r}
filtered_celltype_assignments <- filtered_celltype_assignments |> 
  dplyr::rename(filtered_cellassign_annotations = celltype)

@@

```{r}
# heatmap of prediction scores 
visser_predictions |>
  tibble::column_to_rownames("barcode") |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE,
                     annotation_row = annotation_df)
```

@@

```{r}
# heatmap of prediction scores 
panglao_predictions |>
  tibble::column_to_rownames("barcode") |> 
  as.matrix() |> 
  pheatmap::pheatmap(show_rownames = FALSE,
                     annotation_row = annotation_df)
```
